Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-09 paper.qmd
Langevitour is introduced in page 5

- Make sure langevitour is explained before using it
- Too much code needs to be streamlined
- Remove all the extraneous commented text (Done)
- Check how \kD{} and \gD{} are used, and make sure it's sensible

>>>>

- Make sure langevitour is explained before using it (introduced in page 5)
- Too much code needs to be streamlined
- Remove all the extraneous commented text (Done)
- Check how \kD{} and \gD{} are used, and make sure it's sensible
